Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 2 axes

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            scaled_data = scaled_two_curvy_data, 
                            scaled_data_model = scaled_two_curvy_data_model, 
                            distance_df_small_edges = distance_df_small_edges_two_curvy, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.01))

>>>>

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            scaled_data = scaled_two_curvy_data, 
                            scaled_data_model = scaled_two_curvy_data_model, 
                            distance_df_small_edges = distance_df_small_edges_two_curvy, 
                            axis_param = list(limits = 0.35, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.01))
